%-------------------------
% CV in Latex
% Author : Nuruzzaman Milon
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{1.5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large{#1}} \small{\textit{#4}} & #2 \\
      \textsl{#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textsl{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeCertificate}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\item#1\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape \href{https://milon.im}{Nuruzzaman Milon}} \\ \vspace{3pt}
    \small 
        \textbf{
            \faMapMarker \enspace Vancouver, BC, Canada  $|$
            \href{tel:+16047357681}{\faMobile \enspace +1 (604) 735 7681} $|$ 
            \href{mailto:contact@milon.im}{\faEnvelopeO \enspace contact@milon.im}
        }
        \\
        \vspace{2pt}
        \href{https://milon.im}{\faGlobe \enspace https://milon.im} $|$
        \href{https://linkedin.com/in/tomilon}{\faLinkedinSquare \enspace linkedin.com/in/tomilon} $|$
        \href{https://github.com/milon}{\faGithub \enspace github.com/milon} $|$
        \href{https://twitter.com/to_milon}{\faTwitter \enspace twitter.com/to\_milon}
        
\end{center}

%--------PROFESSIONAL SUMMARY----------
\section{Professional Summary}
    \vspace{-4pt}
    Software Engineer with over a decade of experience across diverse industries. Expertise in all stages of the software development lifecycle, implementing best practices to drive business outcomes. Proven track record of effective collaboration with cross-functional teams to achieve project goals. Key competencies include:
    \vspace{-6pt}
    
    \begin{center}
        Software Development $|$ Architecture $|$ Agile $|$ Innovation $|$ Communication $|$ Leadership $|$ Testing
    \end{center}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://diamondinteractive.ca}{\underline{Diamond Interactive}}} {January 2025 -- Present}
      {Senior Software Engineer}{Vancouver, BC, Canada}
      \resumeItemListStart
        \resumeItem{Rewrote the entire legacy admin panel, replacing it with a modern alternative for two sweepstakes casino platforms: chanced.com and punt.com.}
        \resumeItem{Optimized the entire backend API suite to handle 16k concurrent users.}
        \resumeItem{Developed a new fraud detection mechanism for the user redemption workflow, resulting in a 38\% reduction in fraudulent activities.}
        \resumeItem{Implemented a new load testing infrastructure capable of simulating up to 25k concurrent users, ensuring every new feature maintained performance and stability.}
        \resumeItem{Technologies: PHP, Laravel, PostgreSQL, Redis, React, Docker, AWS, k6}
      \resumeItemListEnd
    
    \resumeSubheading
      {\href{https://amazon.com}{\underline{Amazon Development Centre Canada}}} {December 2023 -- December 2024}
      {Software Development Engineer II}{Vancouver, BC, Canada}
      \resumeItemListStart
        \resumeItem{Contributed as a Software Engineer on the Gift Card Fulfillment and Delivery Charter team, focusing on Amazon Gift Cards.}
        \resumeItem{Migrated the entire Gift Card Organization's email suite to Amazon's new templating system.}
        \resumeItem{Technologies: Java, TypeScript, React, AWS}
      \resumeItemListEnd

      \resumeSubSubheading
        {Software Development Engineer II \small{\textit{Toronto, ON, Canada}}}{February 2023 -- November 2023}
        \resumeItemListStart
           \resumeItem{Worked as a software engineer at Amazon Connections in the UX Tech team.}
        \resumeItemListEnd

    \resumeSubheading
      {\href{https://flix.com}{\underline{Flix}}} {January 2020 -- January 2023}
      {Senior Software Engineer}{Berlin, Germany}
      \resumeItemListStart
        \resumeItem{Managed network inventory, generated rides, and oversaw vehicle circulations for the Flixbus and Flixtrain networks across 38 countries on 4 continents.}
        \resumeItem{Developed a proprietary navigation system for bus drivers within the FlixDriver app, eliminating external dependencies.}
        \resumeItem{Built a lost and found reporting system directly within the FlixDriver app, reducing lost baggage claims by 44\%.}
        \resumeItem{Technologies: PHP, Laravel, Symfony, Java, Kotlin, React Native, Kafka, SQS, MySQL, Docker, AWS, Kubernetes, GitLab CI, React, TypeScript}
      \resumeItemListEnd
      
    \resumeSubheading
      {\href{https://urbansportsclub.com}{\underline{Urban Sports Club}}}{July 2019 -- December 2019}
      {Senior Software Engineer}{Berlin, Germany}
      \resumeItemListStart
        \resumeItem{Created a multi-currency payment system to integrate new payment gateways, facilitating faster growth.}
        \resumeItem{Led the team, with responsibility for financing, payments, and GDPR compliance.}
        \resumeItem{Technologies: PHP, Laravel, Symfony, Phalcon, MySQL, RabbitMQ, Redis, AWS}
    \resumeItemListEnd

    \resumeSubheading
      {\href{http://check24.de}{\underline{Check24}}}{May 2018 -- June 2019}
      {Senior Software Engineer}{Münster, NRW, Germany}
      \resumeItemListStart
        \resumeItem{Developed and maintained tires, car parts, and insurance portals for the Autoteile team, serving over 10 million customers.}
        \resumeItem{Technologies: PHP, Symfony, Laravel, MySQL, Doctrine, React, Elasticsearch}
      \resumeItemListEnd
      
    \resumeSubheading
      {\href{https://telenorhealth.com}{\underline{Telenor Health}}}{May 2016 -- April 2018}
      {Senior Software Engineer}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Created a digital healthcare solution providing affordable health services (medications, information, insurance, etc.) to over 5.5 million people.}
        \resumeItem{Managed a team comprising 4 developers, 3 interns, 1 QA, and 1 DevOps specialist.}
        \resumeItem{Developed a high-traffic SMS gateway capable of handling 3k req/s and enabling inter-app communication via HTTP.}
        \resumeItem{Developed a comprehensive CMS for distributing healthcare information to 10 million people.}
        \resumeItem{Developed a custom tool for queue management, monitoring, and report generation.}
        \resumeItem{Technologies: PHP, Laravel, Lumen, Node.js, Express.js, PostgreSQL, Jenkins, Docker, AWS, Ansible, Angular, XMPP}
      \resumeItemListEnd
      
    \resumeSubheading
      {\href{https://wedevs.com}{\underline{WeDevs Ltd.}}}{February 2015 -- April 2016}
      {Software Engineer}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Developed the Rx71 health service, featuring health articles, a symptom checker, and a doctor and hospital directory with booking and diet plan services.}
        \resumeItem{Managed a team of 6 developers, 2 SQA, and 1 DevOps; served as interim CTO for 3 months.}
        \resumeItem{Technologies: PHP, Laravel, Lumen, WordPress, MySQL, Angular, IonicJS, socket.io}
      \resumeItemListEnd
      
    \resumeSubheading
      {\href{https://brotecs.com}{\underline{Brotecs Technologies Ltd.}}}{September 2013 -- January 2015}
      {Software Engineer}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Built VoIP calling applications for native Android and iOS operating systems.}
        \resumeItem{Developed a web-based GUI for maintaining the Asterisk PABX server.}
        \resumeItem{Created airplane entertainment module for SAP-212 hardware device to enable call, email, and web browsing.}
        \resumeItem{Technologies: PHP, CodeIgniter, Android SDK, Objective-C, Angular, Asterisk}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://itmedicus.com}{\underline{ITMedicus Bangladesh Ltd.}}}{February 2011 -- August 2013}
      {Programmer and System Analyst}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Wrote and managed the codebase, database, and product design; also handled direct client communications.}
        \resumeItem{Developed full-fledged telemedicine software to support custom hardware, providing quality healthcare in rural areas.}
        \resumeItem{Technologies: PHP, MySQL, Redis, jQuery, Bootstrap}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Mawlana Bhashani Science and Technology University}{Tangail, Bangladesh}
      {Bsc Engineering in Information and Communication Technology (ICT)}{}
      \resumeItemListStart
        \resumeItem{President, Society of ICT}
        \resumeItem{Chief Organizer, 1st MBSTU ICT Fest}
        \resumeItem{Member, Rotary Club of MBSTU}
      \resumeItemListEnd
        
  \resumeSubHeadingListEnd


%-----------BOOKS-----------
\section{Books}
  \resumeSubHeadingListStart    
    \resumeSubheading
      {\textbf{Laravel PHP Web Framework}}{May 2015}
      {Dimik Publication (ISBN: 978-984-33-9190-2)} {}
      \resumeItemListStart
        \resumeItem{Published 2 editions, both of which became best-sellers in Bangladesh and West Bengal, India.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
    \resumeItemListStart
      \resumeItem{\textbf{Programming Languages:} PHP, Java, Python, Node}
      \resumeItem{\textbf{Frameworks/Libraries:} Laravel, Symfony, ReactJS, VueJS}
      \resumeItem{\textbf{Web Technologies:} HTML5, CSS3, JavaScript, Typescript}
      \resumeItem{\textbf{Architecture/APIs:} Microservices, REST, GraphQL}
      \resumeItem{\textbf{Project Management:} Agile, Scrum, Kanban}
      \resumeItem{\textbf{Databases:} PostgreSQL, MySQL, SQLite, MongoDB, Redis, Elasticsearch, DynamoDB}
      \resumeItem{\textbf{Message Queues:} Kafka, Beanstalkd, IronMQ, RabbitMQ}
      \resumeItem{\textbf{Testing:} PHPUnit, Pest, PHPSpec, Codeception, Behat, Jest}
      \resumeItem{\textbf{Web Servers:} Nginx, Apache, Caddy}
      \resumeItem{\textbf{Cloud Platforms:} Amazon AWS, Google Cloud Services, Microsoft Azure}
      \resumeItem{\textbf{Version Control:} Git, Jujustu, SVN}
      \resumeItem{\textbf{Methodologies:} Test-Driven Development (TDD), Domain-Driven Design (DDD)}
      \resumeItem{\textbf{DevOps Tools:} Docker, Kubernetes, Jenkins, Ansible}
    \resumeItemListEnd
 

%-----------Certifications-----------
\section{Certifications}
      \resumeItemListStart
        \resumeItem{\href{https://exam.laravelcert.com/is/nuruzzaman-milon/certified-since/2018-01-08}{\underline{Certified Laravel Developer}} -- 2018}
        \resumeItem{\href{https://bcert.me/swoqnnlks}{\underline{Certified Scrum Professional - Developer}} -- 2018}
        \resumeItem{\href{https://bcert.me/swajseym}{\underline{Certified Scrum Professional - ScrumMaster}} -- 2017}
        \resumeItem{\href{https://bcert.me/segniwpnm}{\underline{Advanced Certified Scrum Developer}} -- 2017}
        \resumeItem{\href{https://bcert.me/skctlvko}{\underline{Certified Scrum Developer}} -- 2017}
        \resumeItem{\href{https://bcert.me/snynrkpl}{\underline{Certified ScrumMaster}} -- 2016}
      \resumeItemListEnd

%-----------Miscellaneous-----------
\section{Miscellaneous}
    \resumeSubHeadingListStart
        \resumeSubItem{\textbf{Language}}
            \resumeItemListStart
                \resumeItem{English (C1 level)}
                \resumeItem{Bengali (Mother tongue)}
                \resumeItem{German (A2 level)}
            \resumeItemListEnd

        \resumeSubItem{\textbf{Personality}}
            \resumeItemListStart
                \resumeItem{\href{https://www.16personalities.com/profiles/3db6b8e4630d9}{\underline{ESTJ-A (Assertive Executive)}}}
            \resumeItemListEnd
        
        \resumeSubItem{\textbf{About Me}}
            \resumeItemListStart
                \resumeItem{Best-seller author}
                \resumeItem{Open-source contributor and evangelist}
                \resumeItem{Authored and maintain open-source packages with over 11 million downloads}
                \resumeItem{Conference speaker}
                \resumeItem{Managing the largest PHP community of Bangladesh: \href{https://web.facebook.com/groups/pxperts}{\underline{phpXperts}}}
                \resumeItem{Managing the largest JavaScript community of Bangladesh: \href{https://www.facebook.com/groups/talkjs.net}{\underline{Talk.js}}}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}